Bird beak's elaboration and exploration

### 2022-08-04 Analysis/02-mcmcmcglmmm_analysis.Rmd
Update 02-mcmcmcglmmm_analysis.Rmd

```{r, eval = TRUE}
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.MCMCglmm")
diagnose.mini.chains(shapespace_allbirds_lvl_superorder_order[[1]])
```

@@

>>>>

```{r, eval = TRUE}
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.MCMCglmm")
pdf(file = "../Manuscript/Figures/parameters_ESS_all_birds.pdf", height = 9, width = 4)
diagnose.mini.chains(shapespace_allbirds_lvl_superorder_order[[1]])
dev.off()
```

@@

```{r, eval = TRUE}
load(file = "../Data/Processed/shapespace_passeriformes.MCMCglmm")
pdf(file = "../Manuscript/Figures/parameters_ESS_passeriformes.pdf", height = 9, width = 4)
diagnose.mini.chains(shapespace_passeriformes[[1]])
dev.off()
```
